---
title: "p-value Paper Activity"
format: pdf
---

For their introductory statistics project, a student wants to determine if there is evidence of a difference in average price between products at two grocery stores in town. They have __a lot__ of time so decide to randomly sample 1000 common items at the two stores, record the price of the item at each store (ignoring any sales), and run a matched pairs t-test on the 1000 differences with a significance level of $\alpha = 0.05$. 

They complete all of the steps of their matched pairs t-test correctly. They then write the following conclusion.

We reject the null hypothesis. There is statistically significant evidence that prices of items at store B are higher than prices of items at store A, on average.

#### Your Task

Recall that Wasserstein, Schirm, & Lazar, (2019) had the following recommendations:

_We summarize our recommendations in two sentences totaling seven words: "Accept uncertainty. Be thoughtful, open, and modest." Remember "ATOM."_

Focusing on the first recommendation, _accept uncertainty_, use the following description of uncertainty, summary statistics of the differences, and graph of the student's data to modify the student's conclusion. 

_Uncertainty exists everywhere in research. And, just like with the frigid weather in a Wisconsin winter, there are those who will flee from it, trying to hide in warmer havens elsewhere. Others, however, accept and even delight in the omnipresent cold; these are the ones who buy the right gear and bravely take full advantage of all the wonders of a challenging climate. Significance tests and dichotomized p-values have turned many researchers into scientific snowbirds, trying to avoid dealing with uncertainty by escaping to a "happy place" where results are either statistically significant or not. In the real world, data provide a noisy signal. Variation, one of the causes of uncertainty, is everywhere. Exact replication is difficult to achieve. So it is time to get the right (statistical) gear and "move toward a greater acceptance of uncertainty and embracing of variation" (Gelman 2016)._

## Activity: p-value Paper

```{r}
#| echo: false
#| output: false
#| warning: false
library(tidyverse)
set.seed(41412001)
n <- 1000
store_a <- rexp(n = n, rate = 0.2) |> round(2)
store_b <- store_a + rnorm(n, mean = 0.1, sd = 0.7) 
price_df <- tibble(store_a, store_b) |> 
  mutate(diff = store_b - store_a)
```

```{r}
#| echo: false
#| fig-height: 2.5
ggplot(data = price_df, aes(x = diff)) +
  geom_histogram(bins = 20, colour = "orchid4", fill = "orchid1") +
  theme_minimal(base_size = 18) +
  labs(x = "Price Differences (in Dollars, B minus A)")
```

```{r}
#| echo: true
#| output: true
t.test(diff ~ 1, data = price_df)
price_df |>
  summarise(mean = mean(diff),
            median = median(diff),
            sd = sd(diff),
            prop = mean(diff > 0),
            q1 = quantile(diff, 0.25),
            q3 = quantile(diff, 0.75))
```
